Fictitious Play in Network Aggregative Games

### 2021-05-06 Documents/FP in NAGs/neurips_2020.tex
Figure Captions

  \begin{figure}[t]
    \centering
    \includegraphics[width = 0.7\textwidth]{Figures/ThreePlayerNetwork.png}
    \caption{\label{fig::ThreePlayerNetwork}}
  \end{figure}

@@

  \begin{align}
    A & = - w B^T \\
    C & = - (1 - w) B^T. 
  \end{align}

@@

  \begin{equation}
    C  = - (1 - w) B, 
  \end{equation}

  with no alteration to $A$. The modification itself is small, however it results in the zero-sum assumption being violated. With the same choices of $\beta$ and $w$, this results in the periodic orbit seen in Figure \ref{fig::nonconvergentShapley}. Here, the orbits reach a stable limit cycle which to be centred around the interior NE.

  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.4 \textwidth}
      \includegraphics[width = \textwidth]{Figures/convergentShapley.png}
    \caption{\label{fig::convergentShapley}}
    \end{subfigure}
    \begin{subfigure}[b]{0.4 \textwidth}
      \includegraphics[width = \textwidth]{Figures/nonConvergentShapley.png}
      \caption{\label{fig::nonconvergentShapley}}
    \end{subfigure}
    \caption{\label{fig::Shapley}}
  \end{figure}

  \begin{figure}[t]
    \centering
    \includegraphics[width = 0.7 \textwidth]{Figures/3PlayerChainNoNoise.png}
    \caption{\label{fig::3PlayerChainNoNoise}}
  \end{figure}

>>>>

  \begin{figure}[t]
    \centering
    \includegraphics[width = 0.6\textwidth]{Figures/ThreePlayerNetwork.png}
    \caption{\label{fig::ThreePlayerNetwork} A NA game where the network is defined by a chain of
    three players, as described in Section \ref{sec::NonConv}.}
  \end{figure}

@@

  \begin{align} \label{eq::zeroSumShapley}
    A & = - w B^T \nonumber \\
    C & = - (1 - w) B^T. 
  \end{align}

@@

  \begin{equation} \label{eq::nonzeroSumShapley}
    C  = - (1 - w) B, 
  \end{equation}

  with no alteration to $A$. The modification itself is small, however it results in the zero-sum
  assumption being violated. With the same choices of $\beta$ and $w$, this results in the periodic
  orbit seen in Figures \ref{fig::nonconvergentShapley} and \ref{fig::3PlayerChainNoNoise}. Here,
  the orbits reach a stable limit cycle which to be centred around the interior NE.

  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.45 \textwidth}
      \includegraphics[width = \textwidth]{Figures/convergentShapley.png}
    \caption{\label{fig::convergentShapley}}
    \end{subfigure}
    \begin{subfigure}[b]{0.45 \textwidth}
      \includegraphics[width = \textwidth]{Figures/nonConvergentShapley.png}
      \caption{\label{fig::nonconvergentShapley}}
    \end{subfigure}
    \caption{\label{fig::Shapley} Orbits of the Fictitious Play in the Three Player Chain (c.f.
    Figure \ref{fig::ThreePlayerNetwork}) with payoff matrices given by (a)
    (\ref{eq::zeroSumShapley}) showing convergence to the interior NE (b)
    (\ref{eq::nonzeroSumShapley}) showing cycles around the interior NE.}
  \end{figure}

  \begin{figure}[t]
    \centering
    \includegraphics[width = 0.7 \textwidth]{Figures/3PlayerChainNoNoise.png}
    \caption{\label{fig::3PlayerChainNoNoise} Distance to the Nash Equilibrium strategy along orbits
    of FP showing oscillations which are bounded away from the NE (i.e. they do not cross the NE).
    The x-axis shows logarithmic time since FP includes a factor of $1/t$, which has the effect of
    slowing down the orbit over time.}
  \end{figure}
